Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-18 appendix.tex
AA: niente di che

>>>>

\subsection{Other metrics}
Un'altra interessante metrica potrebbe essere questa: Auhtors of \cite{zitzler_ec00} remark that a desirable property of the Pareto front is the spread of the non-dominated configurations all over the configuration space. In other words, the more similar the non-dominated configuration distribution is to the uniform distribution, the better is the quality of the Pareto front, since we have not been captured by only one possible subset of Pareto configurations but we are able to span all over the configuration space and find configurations whose parameter values differ considerably. Mi aspetto che PS performi bene sotto questo punto di vista. Ovviamente, non so se e' il caso di considerarla ora. Se non e' il caso, puoi spostare questo testo nel file ``appendix.tex'' come possibile spunto futuro. Per quantificare questa cosa, si potrebbe usare come metrica la normalised absolute dispersion error pero' non nello spazio degli obiettivi, ma nello spazio delle configurazioni.
